%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,8pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Anton Schur} \\[7.5pt]
\href{https://github.com/1ast}{\raisebox{-0.05\height}\faGithub\ 1ast} \ $|$ \ 
\href{https://www.linkedin.com/in/anton-schur/}{\raisebox{-0.05\height}\faLinkedin\ Anton Schur} \ $|$ \ 
\href{https://laststranger.t.me}{\raisebox{-0.05\height}\ \faTelegram  \ LastStranger} \ $|$ \ 
\href{mailto:schur2982@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ schur2982@gmail.com} \ $|$ \ 
\href{tel:+375333801179}{\raisebox{-0.05\height}\faMobile \ +375(33)380-11-79} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Interests/ Keywords/ Summary
\section{Summary}
As an Android developer with three years of experience, I have in-depth knowledge of the Android platform and proficiency in Java and Kotlin. I have experience working with tools such as Android Studio, Gradle, and ProGuard. Also, I worked with NFC, GPIO, and encryption, wrote complex algorithms for user location, and implemented best practices in software development, including design patterns and RESTful API principles. I want to obtain a position in professional development where my skills and knowledge are valued and can benefit the organization.

%Experience
\section{Work Experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Android Developer} & \hfill \textit{\small Kate Media} June 2024 - Present \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item Added new features to project, to match customer requirements;
        \item Updated project to newest technologies, build time has been reduced by almost two times;
        \item Fully covered 30 modules and 10 support libraries of app with tests;
        \item Rewrote a lot of API's on project, that fixed some old bugs and reduced development time;
    \end{itemize}
    \end{minipage}
}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Android Developer} & \hfill \textit{\small Heads and Hands} May 2023 - May 2024 \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item Successfully prepared 3 apps for publishing in Google Play;
        \item Refactored ProGuard rules, that reduced build time of release build for 40\%;
        \item Adopted code for multi-app builds (2 apps in one code base);
        \item Changed telemetry API in the app, which reduced analytic network calls by 30\%;
    \end{itemize}
    \end{minipage}
}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Android Developer} & \hfill \textit{\small Science Solutions} Nov 2021 - June 2024 \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item Single-handedly wrote and handed over to the customer app that works with NFC, QR-reading, and custom encryption without documentation;
        \item Realised custom complex algorithm that shows ads depending on location;
        \item Wrote custom player that can show content depending on its type (Text, image, or video);
        \item Optimised processes on the team, reducing decision time by 50\%.
    \end{itemize}
    \end{minipage}
}
\end{tabularx}


%Projects
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Funday} & \hfill \href{https://play.google.com/store/apps/details?id=ru.funday.android.app}{Link to App} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Funday - app for online shopping in a big chain of clothing stores. As a developer on this project, I realized the Profile page and its subpages, product listing, category pages, and parts of ordering. Also, I changed user analytics and telemetry in the app, which reduced network calls, app size, and app loading on the system. I refactored part of the code, that optimized UI and user input and removed any freezing in the app.}  \\
\textbf{PVIS}\\[3.75pt]
\multicolumn{2}{@{}X@{}}{Passengers visual information system - service for displaying ad and useful information in public transport. As a Project Lead, I defined and created the app's architecture. Also, I wrote the most complex algorithms that use the location of transport to show ads, and GPIO integration without any documentation for device, admin, root rights, and player, which can show a lot of custom content (not only video). Also, I wrote all the design, network, and database layers of the app and its main logic.}  \\
\textbf{Controller app}\\[3.75pt]
\multicolumn{2}{@{}X@{}}{Controller app - service for public transport controllers, that work with NFC, QR scanning, custom encryption, and custom complex location algorithm. This app uses a lot of custom technologies, but it can be started and worked on any phone with NFC and a camera. In this app, all custom technologies integration, network, database layer, UI, domain logic, and algorithms were realized by myself.}  \\

\end{tabularx}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
2018 - 2022 & Bachelor's Degree at \textbf{Belarusian State University of Informatics and Radio-electronics, AI faculty} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
Kotlin, Java, SQL, Android SDK, KMP, MV* Architecture, Jetpack libs, Compose Multiplatform, Material Design (2, 3), Koin, Dagger Hilt, Coroutines, Rest API, Ktor, Retrofit2, Okhttp3, Room, SharedPreferances, DataStore, LiveData, Flow, Cicerone, Navigation Component, Glide, Picasso, Coil, Lottie, Firebase, AppMetrica, Sentry, Notion, AppsFlyer, JUnit, Mockito, Espresso

\vfill

\end{document}
